Batch, Off-Policy Apprencticeship Learning

### 2011-03-28 main.tex
Ajout des deux algos, les différences en bleu

\typeout{Batch, Off-Policy Apprenticeship Learning}
\documentclass{article}
\usepackage{ijcai11}
\usepackage{times}
% the following package is optional:
%\usepackage{latexsym} 
\usepackage{amsthm}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{natbib}
\usepackage{graphicx}
\usepackage{subfigure}
%\usepackage{algorithm2e}
\usepackage{algorithm}
\usepackage{algorithmic}

@@

FIXME: Un mot sur pourquoi il est inutile de faire des itérations sur mu directement ?
\begin{figure*}
 \begin{minipage}[t]{.45\textwidth}
 \begin{algorithm}[H]
   \caption{lstd\_ANIRL} 
   \label{alg:lstd_anirl} 
   \begin{algorithmic}[1]
     \STATE $\omega \leftarrow 0$
     \STATE $D_\mu \leftarrow D $
     \STATE $D_\mu.r \leftarrow \psi(D.s)$
     \STATE $\zeta \leftarrow LSTD\mu( D_\mu )$
     \STATE $\mu \leftarrow \zeta^T\psi(s,\pi_\omega(s))$
     \STATE $D_E.r \leftarrow \psi(D_E.s)$
     \STATE $\mu_E \leftarrow LSTD\mu( D_E )$
     \STATE $\theta \leftarrow {\mu_E - \mu\over ||\mu_E - \mu||_2}$
     \STATE $ \bar\mu \leftarrow \mu $
     \STATE $ t \leftarrow ||\mu_E - \bar\mu||_2 $
     \WHILE{$ t > \epsilon $}
     \STATE $D.r \leftarrow \theta^T\psi(D.s)$
     \STATE $ \omega \leftarrow LSPI(D) $
     \STATE $ \mu \leftarrow LSTD\mu( D_\mu, \pi_\omega )$
     \STATE $\bar\mu \leftarrow \bar\mu + { (\mu-\bar\mu)^T (\mu_E-\bar\mu) \over (\mu-\bar\mu)^T (\mu-\bar\mu) } (\mu-\bar\mu) $
     \STATE $\theta \leftarrow 
       {\mu_E - \bar\mu\over ||\mu_E - \bar\mu||_2}$
     \ENDWHILE
   \end{algorithmic}
 \end{algorithm}
 \end{minipage}
 \hfill
 \begin{minipage}[t]{.45\textwidth}
   \begin{algorithm}[H]
     \caption{Mission-side2 Greedy} 
     \label{alg2} 
     \begin{algorithmic}[1]
       \STATE whatever your alg does
       \FOR{each mission $M_{j}$ in sorted order} 
       \STATE do something
       \ENDFOR
     \end{algorithmic}
   \end{algorithm}
 \end{minipage}
 \hfill
\end{figure*}

@@

FIXME: Dérouler les deux algorithmes complets côte à côte dans une forme lisible, car c'est un peu la galère en lisant le papier d'Abbeel.
\section{Analysis}
FIXME: Matthieu ?
\section{Experimental benchmark}
The experimental benchmark chosen here is the same as in \citep{ng2000algorithms}, a 5x5 grid world. The agent is in one of the case of the grid (whose coordinates is the state) and can choose at each step one of the four compass directions (the action). With probability 0.9, the agent moves in the intended direction. With probability 0.1, the direction is randomly drawn (and thus have probability 0.25 to match the original direction). The expert policy maximizes the following reward : 0 everywhere but in the upper-right square, where it is 1. An episodes ends when the upper right square is attained, or after 20 steps. At the start of each episode, the expert is in the lower-left corner of the grid (the opposite of where the reward is).\\

>>>>

\typeout{Batch, Off-Policy Apprenticeship Learning}
\documentclass{article}
\usepackage{ijcai11}
\usepackage{times}
\usepackage{color}
% the following package is optional:
%\usepackage{latexsym} 
\usepackage{amsthm}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{natbib}
\usepackage{graphicx}
\usepackage{subfigure}
%\usepackage{algorithm2e}
\usepackage{algorithm}
\usepackage{algorithmic}

@@

FIXME: Un mot sur pourquoi il est inutile de faire des itérations sur mu directement ?
\begin{figure*}
 \begin{minipage}[t]{.45\textwidth}
 \begin{algorithm}[H]
   \caption{lstd\_ANIRL} 
   \label{alg:lstd_anirl} 
   \begin{algorithmic}[1]
     \STATE $\omega \leftarrow 0$
     {\color{blue}
     \STATE $D_\mu \leftarrow D $
     \STATE $D_\mu.r \leftarrow \psi(D.s)$
     \STATE $\zeta \leftarrow LSTD\mu( D_\mu, \pi_\omega )$
     \STATE $\mu \leftarrow \zeta^T\phi(s_0,\pi_\omega(s_0))$
     \STATE $D_E.r \leftarrow \psi(D_E.s)$
     \STATE $\zeta \leftarrow LSTD\mu( D_E )$ 
     \STATE $\mu_E \leftarrow \zeta^T\phi(D_E.s_0, D_E.a_0)$
     }
     \STATE $\theta \leftarrow {\mu_E - \mu\over ||\mu_E - \mu||_2}$
     \STATE $ \bar\mu \leftarrow \mu $
     \STATE $ t \leftarrow ||\mu_E - \bar\mu||_2 $
     \WHILE{$ t > \epsilon $}
     \STATE $D.r \leftarrow \theta^T\psi(D.s)$
     \STATE $ \omega \leftarrow LSPI( D, \omega_0 ) $
     {\color{blue}
     \STATE $ \zeta \leftarrow LSTD\mu( D_\mu, \pi_\omega )$   
     \STATE $ \mu \leftarrow \zeta^T\phi(s_0,\pi_\omega(s_0))$}
     \STATE $\bar\mu \leftarrow \bar\mu + { (\mu-\bar\mu)^T (\mu_E-\bar\mu) \over (\mu-\bar\mu)^T (\mu-\bar\mu) } (\mu-\bar\mu) $
     \STATE $\theta \leftarrow 
       {\mu_E - \bar\mu\over ||\mu_E - \bar\mu||_2}$
     \STATE $ t\leftarrow ||\mu_E - \bar\mu||_2$
     \ENDWHILE
   \end{algorithmic}
 \end{algorithm}
 \end{minipage}
 \hfill
 \begin{minipage}[t]{.45\textwidth}
   \begin{algorithm}[H]
   \caption{mc\_ANIRL} 
   \label{alg:mc_anirl} 
   \begin{algorithmic}[1]
     \STATE $\omega \leftarrow 0$
     {\color{blue}
     \STATE $D_\pi \leftarrow simulator( \omega )$
     \STATE $\mu \leftarrow \sum\limits_{s\in D_\pi.s}\psi(s)$
     \STATE $\mu_E \leftarrow \sum\limits_{s\in D_E.s}\psi(s)$
     }
     \STATE $\theta \leftarrow {\mu_E - \mu\over ||\mu_E - \mu||_2}$
     \STATE $ \bar\mu \leftarrow \mu $
     \STATE $ t \leftarrow ||\mu_E - \bar\mu||_2 $
     \WHILE{$ t > \epsilon $}
     \STATE $D.r \leftarrow \theta^T\psi(D.s)$
     \STATE $ \omega \leftarrow LSPI( D, \omega_0 ) $
     {\color{blue}
     \STATE $D_\pi \leftarrow simulator( \omega )$
     \STATE $\mu \leftarrow \sum\limits_{s\in D_\pi.s}\psi(s)$
     }
     \STATE $\bar\mu \leftarrow \bar\mu + { (\mu-\bar\mu)^T (\mu_E-\bar\mu) \over (\mu-\bar\mu)^T (\mu-\bar\mu) } (\mu-\bar\mu) $
     \STATE $\theta \leftarrow 
       {\mu_E - \bar\mu\over ||\mu_E - \bar\mu||_2}$
     \STATE $ t\leftarrow ||\mu_E - \bar\mu||_2$
     \ENDWHILE
     \end{algorithmic}  
   \end{algorithm}
 \end{minipage}
 \hfill
 \caption{Both algorithms side by side, with specific parts in blue}
\end{figure*}

@@

FIXME: Dérouler les deux algorithmes complets côte à côte dans une forme lisible, car c'est un peu la galère en lisant le papier d'Abbeel.
\section{Analysis}
FIXME: Matthieu ?
\section{Experimental benchmark}
The experimental benchmark chosen here is the same as in \citep{ng2000algorithms}, a 5x5 grid world. The agent is in one of the case of the grid (whose coordinates is the state) and can choose at each step one of the four compass directions (the action). With probability 0.9, the agent moves in the intended direction. With probability 0.1, the direction is randomly drawn (and thus have probability 0.25 to match the original direction). The reward optimized by the expert is 0 everywhere but in the upper-right square, where it is 1. For every policy, an episodes ends when the upper right square is attained, or after 20 steps. At the start of each episode, the agent is in the lower-left corner of the grid (the opposite of where the reward is).\\
